Family Fortunes: A Quantitative Analysis of the Early Iron Age Cemeteries at Knossos, Crete

### 2019-03-18 analysis/paper/paper.Rmd
mini changes
reconnected
data added and code begun

```{r, setup, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  comment = "#>",
  fig.path = "../figures/"
)

@@

```{r flowers, fig.cap="Here are some flower measurements"}
library(ggplot2)
ggplot(iris,aes(Sepal.Width,Sepal.Length))+geom_point()
```

>>>>

```{r setup}
knitr::opts_knit$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  comment = "#>",
  fig.path = "../figures/"
)

@@

```{r flowers, fig.cap="Here are some flower measurements"}

library(ggplot2)

pots<-read.csv("../data/raw_data/KnossosPots.csv",header=T)

ggplot(pots,aes(pots$ave_date))+geom_histogram()+xlim(1100,600)
```
